% use the answers clause to get answers to print; otherwise leave it out.
%\documentclass[12pts,answers]{exam}
\documentclass[12pts]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace}
\usepackage{graphicx}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems
% end up in the "middle" of the page, reducing the amount of space for students
% to work on them.
\usepackage[margin=1in]{geometry}
\usepackage{enumerate}
\usepackage[hidelinks]{hyperref}

% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{NPRE 555}
\newcommand{\term}{Fall 2023}
\newcommand{\assignment}{CP 01}
\newcommand{\duedate}{2023.10.11}
%\newcommand{\timelimit}{50 Minutes}

\newcommand{\nth}{n\ensuremath{^{\text{th}}} }
\newcommand{\ve}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\Macro}{\ensuremath{\Sigma}}
\newcommand{\vOmega}{\ensuremath{\hat{\Omega}}}

% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

%\unframedsolutions

\begin{document}

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\assignment\ - Page \thepage\ of \numpages}{Due \duedate}
\runningheadrule

\class \hfill \term \\
\assignment \hfill Due \duedate\\
\rule[1ex]{\textwidth}{.1pt}
%\hrulefill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
        \item Show your work.
        \item Please submit your assignment online via github classroom at
          \url{https://classroom.github.com/a/XXYpSyAn}
        \item All code must be version controlled with git.
        \item You may discuss your process with your peers, but your
          implementation and code should stand alone. This assignment is
          individual work.
\end{itemize}
\rule[1ex]{\textwidth}{.1pt}

% ---------------------------------------------
\begin{questions}
        \question[30] Write a Monte Carlo code to calculate the multiplication
constant and flux distribution for one-speed neutrons in a
slab reactor of thickness $a = 1.0 m$ with isotropic scattering
for which ($\Sigma_a = 0.12 cm^{-1}$, $\Sigma_s = 0.05 cm^{-1}$,
$\nu\Sigma_f= 0.15 cm^{-1}$) over $0 <x< 50 cm$ and ($\Sigma_a = 0.10 cm^{-1}$,
        $s = 0.05 cm^{-1}$, $\nu\Sigma_f = 0.12 cm^{-1}$) over $50 <x< 100 cm$.

        \question[30] Report on your results with sufficient clarity to reproduce
        your work. This should include:
        \begin{parts}
          \part a clear README describing how your instructor can replicate your flux distribution plot and multiplication
        factor.
          \part A report document (in any format, but markdown or latex are
        preferred) should include a 5 page description of your methodology,
        results, and observations on your work.
        Your report document should provide include citations to
        references that you used.
        \end{parts}

	      \question Employ good software practices.
        \begin{parts}
                \part[10] Use functions, data structures, and classes appropriately.
                \part[10] Document your code clearly, using informative
                variable names, documentation strings, and function call
                definitions.
                \part[10] Include a license. Consider BSD-3, a permissive open
                source licence that requests attribution only.
                \part[10] The code and repository should be well
                organized, readable, and runnable.
        \end{parts}

\end{questions}



%\bibliographystyle{plain}
%\bibliography{hw01}
\end{document}
